Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-02 _tex/index.tex
Built site for gh-pages

Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities \citep{colburnDiscontinuitiesSolarWind1966}, embody localized transient rotations or jumps of the magnetic field. Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere \citep{liuCategorizingMHDDiscontinuities2022} to the heliosheath \citep{burlagaCurrentSheetsHeliosheath2011}. Theoretical models \citep[\citet{medvedevDissipativeDynamicsCollisionless1997}]{lerchePropagationMagneticDisturbances1975} and MHD simulations \citep[\citet{grecoStatisticalAnalysisDiscontinuities2009}, \citet{yangFormationRotationalDiscontinuities2015}]{grecoIntermittentMHDStructures2008} suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence. These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles \citep{wentzelMotionMagneticDiscontinuities1964}. Moreover, they contribute significantly to the magnetic fluctuation spectra \citep{borovskyContributionStrongDiscontinuities2010} and can affect space weather \citep{tsurutaniReviewInterplanetaryDiscontinuities2011}. Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities. However, previous study of solar wind discontinuities evolution \citep{sodingRadialLatitudinalDependencies2001} in the outer heliosphere were rarely in conjunction with measurements closer to the Sun. Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum. Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.

>>>>

Rapid variations in interplanetary magnetic fields, commonly recognized as solar wind magnetic discontinuities \citep{colburnDiscontinuitiesSolarWind1966}, embody localized transient rotations or jumps of the magnetic field. Considered important for efficient plasma heating, they carry the most intense currents found in the solar wind and obserrved throughout the heliosphere from inner heliosphere \citep{liuCategorizingMHDDiscontinuities2022} to the heliosheath \citep{burlagaCurrentSheetsHeliosheath2011}. Theoretical models \citep{lerchePropagationMagneticDisturbances1975, medvedevDissipativeDynamicsCollisionless1997} and MHD simulations \citep{grecoIntermittentMHDStructures2008, grecoStatisticalAnalysisDiscontinuities2009, yangFormationRotationalDiscontinuities2015} suggest that the formation and destruction of discontinuities are closely related to the nonlinear dynamics of Alfvén waves and/or Alfvénic turbuluence. These nonlinear processes can create significant isolated disturbances to the otherwise adiabatic evolution of the solar wind flow (?Reference?) and host many processes, including magnetic reconnection (?Reference?) and Fermi acceleration of particles \citep{wentzelMotionMagneticDiscontinuities1964}. Moreover, they contribute significantly to the magnetic fluctuation spectra \citep{borovskyContributionStrongDiscontinuities2010} and can affect space weather \citep{tsurutaniReviewInterplanetaryDiscontinuities2011}. Therefore, the study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind and test the local generation mechanism of discontinuities. However, previous study of solar wind discontinuities evolution \citep{sodingRadialLatitudinalDependencies2001} in the outer heliosphere were rarely in conjunction with measurements closer to the Sun. Moreover, the intervals in their study spread over multiple solar cycles though they are selected during solar activity minimum. Thus it is presently unclear whether their frequency and properties are the result of solar variability or due to the natural evolution of the discontinuities during their propagation and interaction with the ambient solar wind.
